Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-05-11 _paper.rmd
conclusions - more changes

This analysis is manually intensive and thus only feasible for investigating a few instances. The approach selects instances that the model has not done well to predict and compare it with an instance where it did fit well. The radial tour launches from the attribution projection to enable exploration of the sensitivity of the prediction to any feature. It can be helpful to make additional plots of the features and responses to cross-check interpretations made from the cheem viewer. This methodology provides an additional tool in the box for studying model fitting.

>>>>

This analysis is manually intensive and thus only feasible for investigating a few instances. The recommended approach is to investigate an instance where the model has not predicted accurately and compare it with an instance with similar predictor values where model fitted well. The radial tour launches from the attribution projection to enable exploration of the sensitivity of the prediction to any feature. It can be helpful to make additional plots of the features and responses to cross-check interpretations made from the cheem viewer. This methodology provides an additional tool in the box for studying model fitting.
